Open source landscape ecology tools \thanks{Grants or other notes about the article that should go on the front page should be placed here. General acknowledgments should be placed at the end of the article.}

### 2020-07-08 paper/paper.Rmd
Starting to write on general introduction

# Introduction {#intro}

Landscape ecology does this and that \cite{turner2005}.

# Section title {#sec:1}

Open-source is great \cite{sandve2013}.

## Subsection title {#sec:2}

as required. Don't forget to give each section
and subsection a unique label (see Sect. \ref{sec:1}).

>>>>

# Introduction {#sec:intro}

## A short introduction to landscape ecology {#sec:landscape_ecology}

Landscape ecology focuses on how ecological processes are influenced and modified by the heterogeneous landscapes they occur in and simultaneously how the ecological processes themselves influence the landscapes \cite{Turner1989,Turner2005,With2019}. In this context, landscape ecology considers, besides others, spatial and temporal dynamics of heterogeneous landscapes, interactions, fluxes and exchange within these landscapes, how the landscapes influence ecological processes (and vice versa) and lastly how to manage these heterogeneous landscapes \cite{Risser1984,Turner1989}.

While human activities have altered their environment for millennials \cite{Ellis2011}, in the past centuries the effects of humans on the global environment have increased to an unknown high, known as the the Anthropocene \cite{Crutzen2002}. Today, almost all ecosystems are directly or indirectly influenced by human activities \cite{Vitousek1997}. Thus, understanding the complex interactions between landscapes and ecological processes also becomes more important \cite{With2019}.

Because landscapes are defined as mosaics of different land covers, ecosystems, habitat types, or land uses \cite{Forman1986,Forman1995}, spatial context is important and ecological processes will vary spatially \cite{With2019}. Thus, in contrast to many other sub-disciplines of ecology, landscape ecology emphasizes spatial patterns \cite{Risser1984}. Consequently, the field of landscape ecology relies on tools to preprocess, modify, model, analyze and visualize spatial data.

## Open-source software and R {#sec:open_source}

Open-source software includes all software which is released under a license that allows to freely use, modify and distribute the software \cite{St.Laurent2008}. Open-source software development has many advantages, such as fast innovation, transparency and reliability as well as longevity due to many diverse contributors \cite{vonKrogh2006,St.Laurent2008}.

One example of a successful open-source project is the R programming language and its *Comprehensive R Archive Network* (CRAN) for extensions (also called packages) \cite{RCoreTeam2019}. Firstly introduced in 1995 \cite{Smith2016}, today the programming language is among the most popular programming languages, especially in ecology \cite{Lai2019}.

## Landscape ecology in R {#sec:R}

### 2020-07-08 paper/paper.tex
Starting to write on general introduction

\hypertarget{intro}{%
\section{Introduction}\label{intro}}

Landscape ecology does this and that \cite{turner2005}.

\hypertarget{sec:1}{%
\section{Section title}\label{sec:1}}

Open-source is great \cite{sandve2013}.

\hypertarget{sec:2}{%
\subsection{Subsection title}\label{sec:2}}

as required. Don't forget to give each section and subsection a unique
label (see Sect. \ref{sec:1}).

>>>>

\hypertarget{sec:intro}{%
\section{Introduction}\label{sec:intro}}

\hypertarget{sec:landscape_ecology}{%
\subsection{A short introduction to landscape
ecology}\label{sec:landscape_ecology}}

Landscape ecology focuses on how ecological processes are influenced and
modified by the heterogeneous landscapes they occur in and
simultaneously how the ecological processes themselves influence the
landscapes \cite{Turner1989,Turner2005,With2019}. In this context,
landscape ecology considers, besides others, spatial and temporal
dynamics of heterogeneous landscapes, interactions, fluxes and exchange
within these landscapes, how the landscapes influence ecological
processes (and vice versa) and lastly how to manage these heterogeneous
landscapes \cite{Risser1984,Turner1989}.

While human activities have altered their environment for millennials
\cite{Ellis2011}, in the past centuries the effects of humans on the
global environment have increased to an unknown high, known as the the
Anthropocene \cite{Crutzen2002}. Today, almost all ecosystems are
directly or indirectly influenced by human activities
\cite{Vitousek1997}. Thus, understanding the complex interactions
between landscapes and ecological processes also becomes more important
\cite{With2019}.

Because landscapes are defined as mosaics of different land covers,
ecosystems, habitat types, or land uses \cite{Forman1986,Forman1995},
spatial context is important and ecological processes will vary
spatially \cite{With2019}. Thus, in contrast to many other
sub-disciplines of ecology, landscape ecology emphasizes spatial
patterns \cite{Risser1984}. Consequently, the field of landscape ecology
relies on tools to preprocess, modify, model, analyze and visualize
spatial data.

\hypertarget{sec:open_source}{%
\subsection{Open-source software and R}\label{sec:open_source}}

Open-source software includes all software which is released under a
license that allows to freely use, modify and distribute the software
\cite{St.Laurent2008}. Open-source software development has many
advantages, such as fast innovation, transparency and reliability as
well as longevity due to many diverse contributors
\cite{vonKrogh2006,St.Laurent2008}.

One example of a successful open-source project is the R programming
language and its \emph{Comprehensive R Archive Network} (CRAN) for
extensions (also called packages) \cite{RCoreTeam2019}. Firstly
introduced in 1995 \cite{Smith2016}, today the programming language is
among the most popular programming languages, especially in ecology
\cite{Lai2019}.

\hypertarget{sec:R}{%
\subsection{Landscape ecology in R}\label{sec:R}}
